Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-04 manuscript.Rmd
centroids

```{r join_sf}
travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

centroids <- cbind(st_coordinates(st_centroid(travel_time_sf)))
```

```{r}
plot(st_geometry(dc_acs_tracts), border="grey")
plot(st_centroid(st_geometry(dc_acs_tracts), of_largest_polygon), add=TRUE, col="blue")
```

@@

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	geom_sf(data = dc_roads) +
	theme_map +
	scale_fill_viridis_c(direction = -1) 
```

@@

```{r}
travel_time_sf %>% 
  mutate(state = substr(geo2010, start = 1, stop = 2)) %>%
  mutate(tract_number = substr(geo2010, start = 10, stop = 1000)) %>%
```

>>>>

```{r join_sf}
centroids <- data.frame(cbind(st_coordinates(st_centroid(dc_acs_tracts))))

centroids <- centroids %>% 
  mutate(GEOID = dc_acs_tracts$GEOID)

dc_acs_tracts <- left_join(x = dc_acs_tracts, y = centroids, by = "GEOID")

travel_time_sf <- left_join(x = travel_times_census_join, y = dc_acs_tracts, by = "GEOID") %>%
	st_as_sf() %>%
	st_transform(crs = 102285) 
```

@@

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	geom_sf(data = dc_roads) +
  geom_sf(data = st_centroid(st_geometry(travel_time_sf), of_largest_polygon)) + 
	theme_map +
	scale_fill_viridis_c(direction = -1) 
```

@@
